Supporting Information: Chemically Selective Transport in a Cross-linked H\textsubscript{II} Phase Lyotropic Liquid Crystal Membrane

### 2019-05-08 Ben_Manuscripts/transport/Draft.tex
updated tex.
Moved spatial density figure to main text

% MRS2: I think it would be useful to have a picture of the pores to 
% allow people to visualize what was going on. ToC might be good, 
% but I think that as people read, they need to see the 3D picture 
% as well to think through things.

@@

  %BJC4: generalized to amphiphilic self-assembled structures.
  Under the right conditions, amphiphilic molecules can self-assemble into
  ordered nanostructures that may be capable of performing highly selective
  separations with permeabilities comparable to NF.
  \begin{itemize}
    \item The uniform-sized aqueous pores characteristic of these types of
    systems enforce a molecular-size cut-off, eliminating issues related to the
    polydisperity of NF pores.
    \item In addition to size-exclusion, it may be possible to control the
    chemical environment within the nanopores by altering the identities of the
    hydrophilic moeties that form the pores, affording solute-specific separations.
  \end{itemize}

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.
  \begin{itemize}
	\item When cross-linked, these materials can function as mechanically
	strong separations membranes.
	\item The H\textsubscript{II} phase has hexagonally packed, straight
	pores which is the ideal geometry for high throughtput separations.
	\item However, the synthesis of H\textsubscript{II} membranes with 
	highly aligned hexagonal mesophases has been a challenge that has 
	prevented the material's viability as a separations membrane.
	\item The Q\textsubscript{I} consists of a three dimensional network
	of tortuous and interconnected pores. 
	\item It's more facile synthesis has yielded it more success
	\item The latest Q\textsubscript{I} phase membranes have been shown
	to exhibit selectivities and permeabilities higher than commercial
	RO and NF membranes.
  \end{itemize}

  % Highlight that QI has the best chance.
  Although Q\textsubscript{I} membranes have shown promising results, it
  is not clear how to controllably design them for specific separations
  beyond what has already been achieved.
  \begin{itemize}
    \item Dischinger et al. found that they do not separate purely on the basis
    of size.~\cite{dischinger_effect_2017} 
    \item Empirical modeling revealed correlations between various solute
    physicochemical properties and observed solute rejection. 
    \item Although there was some agreement with their empirical model, it does not
    offer a sufficiently detailed explanation of governing molecular interactions.~\cite{dischinger_effect_2017}
  \end{itemize}

@@

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibrations that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density as well
  as oxygen atoms at the ends of each monomer tail which can further stabilize
  water molecules. See Figure~\ref{S-fig:total_density} of the Supporting 
  Information for a graphical illustration of this point.

@@

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try. Broke into paragraphs
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes. 
  %MRS3: I'd actually suggest connecting these; since above is a thesis statement for the next bit. 
  Since solutes move slowly while entangled among the monomer tails,
  and since more than half of the solutes studied spend at least 40\% of their
  time in the tails, one can try to design monomers that better control the 
  partition of solutes between the pore and tail region. Solutes move into 
  the tails due both to their size and hydrophilic character. One may be 
  able to contain solutes, even small ones like methanol, by increasing
  the density of monomers close to the head groups through incorporation of 
  cross-linkable groups in the vicinity. Alternatively, removal of the ether
  linkages between the head groups and the monomer tails may decrease the 
  stability of any of the molecules we studied near the head groups and 
  force them to spend more time within the pore.

>>>>

@@

  %BJC4: generalized to amphiphilic self-assembled structures.
  Under the right conditions, amphiphilic molecules can self-assemble into
  ordered nanostructures that may be capable of performing highly selective
  separations with permeabilities comparable to NF.~\cite{alexandridis_amphiphilic_2000}
  The uniform-sized aqueous pores characteristic of these types of systems 
  enforce a molecular-size cut-off, eliminating issues related to the 
  polydisperity of NF pores.~\cite{zhou_supported_2005} In addition to size-exclusion,
  it may be possible to control the chemical environment within the nanopores by
  altering the identities of the hydrophilic moieties that form the pores, 
  affording solute-specific separations.~\cite{dischinger_effect_2017}

  %BJC4: bring it back to LLCs but don't make it seem like HII is the best
  Amphiphilic lyotropic liquid crystals (LLCs) are known to form the type I 
  bicontinuous (Q\textsubscript{I}) and inverted hexagonal (H\textsubscript{II})
  phases.~\cite{smith_ordered_1997,dischinger_application_2017,carter_glycerol-based_2012,hatakeyama_nanoporous_2010} 
  When cross-linked, these materials can function as mechanically
  strong separations membranes.~\cite{zhou_supported_2005} The H\textsubscript{II}
  phase has hexagonally packed, straight pores which is the ideal geometry 
  for high throughtput separations. However, the synthesis of H\textsubscript{II}
  membranes with highly aligned hexagonal mesophases has been a challenge that
  has been met with limited success and has prevented the material's viability 
  as a separations membrane.~\cite{feng_scalable_2014,feng_thin_2016} The Q\textsubscript{I} 
  consists of a three dimensional network of tortuous and interconnected pores. 
  It's more facile synthesis has yielded it more success. The latest 
  Q\textsubscript{I} phase membranes have been shown to exhibit selectivities
  higher than commercial NF and RO membranes permeabilities higher than commercial
  RO membranes.~\cite{dischinger_application_2017}

  % Highlight that QI has the best chance.
  Although Q\textsubscript{I} membranes have shown promising results, it
  is not clear how to controllably design them for specific separations
  beyond what has already been achieved. Dischinger et al. found that they
  do not separate purely on the basis of size. Empirical modeling revealed
  correlations between various solute physicochemical properties and 
  observed solute rejection. Although there was some agreement with their
  empirical model, it does not offer a sufficiently detailed explanation
  of governing molecular interactions.~\cite{dischinger_effect_2017}

@@

  There is an appreciable amount of water that partitions into the distal tail
  region of both systems. 28\% and 31\% of the total water is present in the
  distal tail regions of the 5 and 10 wt\% water systems respectively. See 
  Section~\ref{S-section:water_content_equil} of the Supporting Information 
  for more details on the equilibrations that led to this conclusion. The partition
  is due to a combination of the distal tail region's lower density (see 
  Figure~\ref{fig:total_density})as well as oxygen atoms at the ends of each
  monomer tail which can further stabilize water molecules.

  %See Figure~\ref{S-fig:total_density} of the Supporting 
  %Information for a graphical illustration of this point.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \vspace{-0.5cm}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{Looking down at the $xy$ plane of the LLC membranes, the lowest density regions
  of both membranes are in the pore center and in the tail region, furthest from the pore
  center (a \& c). Water is densest in the low density regions (b \& d).}\label{fig:total_density}
  \end{figure}

@@

  %MRS2: trying something else to emphasize what we are trying to do.  Can you add a bit more detail so it's not just slowing up or speeding solutes, but slowing or speeding up solutes of a particular type?  We can emphasize chemical selectivity . . . 
  %mitigate or enhance their effect on   solute MSDs.   
  %BJC3: gave it a try. Broke into paragraphs
  Based on these trapping mechanisms, we may be able to suggest modifications
  that can be made to monomers that will modulate their effect on specific 
  solute MSDs in order to make transport even more selective for particular 
  solutes. Since solutes move slowly while entangled among the monomer tails,
  and since more than half of the solutes studied spend at least 40\% of their
  time in the tails, one can try to design monomers that better control the 
  partition of solutes between the pore and tail region. Solutes move into 
  the tails due both to their size and hydrophilic character. One may be 
  able to contain solutes, even small ones like methanol, by increasing
  the density of monomers close to the head groups through incorporation of 
  cross-linkable groups in the vicinity. Alternatively, removal of the ether
  linkages between the head groups and the monomer tails may decrease the 
  stability of any of the molecules we studied near the head groups and 
  force them to spend more time within the pore.

### 2019-05-08 Ben_Manuscripts/transport/Supporting_Information.tex
Moved spatial density figure to main text

  \clearpage
  \section{Total Membrane Density}\label{section:total_density}

  In our simulations, we observe that water partitions into the tail region
  because of the tails' low density. We plotted the density of all atoms in 
  the system as function of their $xy$ positions within the unit cell. The 
  pore centers of the 5 and 10 wt \% water systems have a relatively low density
  that is comparable to the density in the tails far from the pore center
  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
  The density is highest near the middle of the tails. The observed density distribution
  is necessary in order for the wedge-shaped monomers to fill space and stay in
  the hexagonal phase. Accordingly, water is densest in the pore center and at 
  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
  dense mid-tail region.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
  \end{subfigure}
  \caption{The lowest density regions of both membranes are in the pore center and in the
  tail region, furthest from the pore center (a \& c). Water is densest in the low density
  regions (b \& d).}\label{fig:total_density}
  \end{figure}

>>>>

%  \clearpage
%  \section{Total Membrane Density}\label{section:total_density}
%  BJC: moved to main text
%  
%  In our simulations, we observe that water partitions into the tail region
%  because of the tails' low density. We plotted the density of all atoms in 
%  the system as function of their $xy$ positions within the unit cell. The 
%  pore centers of the 5 and 10 wt \% water systems have a relatively low density
%  that is comparable to the density in the tails far from the pore center
%  (see figures~\ref{fig:total_density_5wt} and~\ref{fig:total_density_10wt}).
%  The density is highest near the middle of the tails. The observed density distribution
%  is necessary in order for the wedge-shaped monomers to fill space and stay in
%  the hexagonal phase. Accordingly, water is densest in the pore center and at 
%  the tail ends (see figures~\ref{fig:total_water_density_5wt} 
%  and~\ref{fig:total_water_density_10wt}). Very little water is present in the 
%  dense mid-tail region. 
%  
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{total_density_5wt.pdf}
%  \caption{5 wt \% water, spatial density of all atoms}\label{fig:total_density_5wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{total_water_density_5wt.pdf}
%  \caption{5 wt \% water, spatial density of water}\label{fig:total_water_density_5wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{total_density_10wt.pdf}
%  \caption{10 wt \% water, spatial density of all atoms}\label{fig:total_density_10wt}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{total_water_density_10wt.pdf}
%  \caption{10 wt \% water, spatial density of water}\label{fig:total_water_density_10wt}
%  \end{subfigure}
%  \caption{The lowest density regions of both membranes are in the pore center and in the
%  tail region, furthest from the pore center (a \& c). Water is densest in the low density
%  regions (b \& d).}\label{fig:total_density}
%  \end{figure}
